Supporting Awareness of Indirect Conflicts with Impact

### 2013-12-09 impact-uvic-2013/paper.tex
IMPACT completed uvic technical paper.

\usepackage{graphicx}
\usepackage{amsmath}

@@

@@

\section{Introduction}
Awareness is characterized as "an understanding of the activities of others
which provides a context for one's own activities"~\cite{Dourish:1992:ACS}.
The study of awareness and its tools has become an important topic of
research in software engineering especially with the new importance of
distributed work and collaboration. Awareness is generally associated with
both technical and social dependencies that are created and evolve over
a software project's life time. The study of these dependencies has become
the primary focus of most awareness related research. Task awareness has
become the most prevalent field of awareness research to understand 
how developers cope with these technical and social dependencies.

@@

Indirect conflicts arising in source code are inherently
difficult to resolve as most of the time, source code analysis or
program slicing~\cite{Weiser:1981:PS} must
be performed in order to find relationships between technical objects
which are harmed by changes.
While some awareness tools have been created with these indirect conflicts
primarily in mind~\cite{Begel:2010:CDE, Trainer:2005:BGT}, most have only 
created an exploratory environment which is used by developers to
solve conflicts which may arise. These tools were not designed to detect
indirect conflicts that arise and alert developers to their presence 
inside the software system. Sarma et al.~\cite{Sarma:2007:TSA} has started to work directly
on solving indirect conflicts, however, these products are not designed to handle
internal structures of technical objects.

>>>>

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{fancyhdr}

@@

\pagestyle{fancy}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{University of Victoria Computer Science Technical Paper: DCS-351-IR}
\fancyfoot[C]{}

\fancypagestyle{firststyle}
{
   \fancyhf{}
   \renewcommand{\headrulewidth}{0pt}
   \fancyfoot[C]{}
   \rfoot{University of Victoria Computer Science Technical Paper: DCS-351-IR}
}

@@

\section{Introduction}
\thispagestyle{firststyle}
Awareness is characterized as "an understanding of the activities of others
which provides a context for one's own activities"~\cite{Dourish:1992:ACS}.
The study of awareness and its tools has become an important topic of
research in software engineering especially with the new importance of
distributed work and collaboration. Awareness is generally associated with
both technical and social dependencies that are created and evolve over
a software project's life time. The study of these dependencies has become
the primary focus of most awareness related research. Task awareness has
become the most prevalent field of awareness research to understand 
how developers cope with these technical and social dependencies.

@@

Indirect conflicts arising in source code are inherently
difficult to resolve as most of the time, source code analysis or
program slicing~\cite{Weiser:1982:PUS} must
be performed in order to find relationships between technical objects
which are harmed by changes.
While some awareness tools have been created with these indirect conflicts
primarily in mind~\cite{Begel:2010:CDE, Trainer:2005:BGT}, most have only 
created an exploratory environment which is used by developers to
solve conflicts which may arise. These tools were not designed to detect
indirect conflicts that arise and alert developers to their presence 
inside the software system. Sarma et al.~\cite{Sarma:2007:TSA} has started to work directly
on solving indirect conflicts, however, these products are not designed to handle
internal structures of technical objects.
